Enhancement of SDR in Thessaloniki

### 2024-04-09 GHI_enh_04_investigate.tex
Commit 2024-03-28 12:14
Commit 2024-04-07 21:13
Commit 2024-04-09 16:18

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-28}

@@

@@

Arima: -0.013183 +/- 6.898051

@@

Arima: 1.03413 +/- 0.363494

@@

Arima: 0.944623 +/- 0.38704

@@

Arima: 33.721354 +/- 8.881986

@@

@@

\begin{verbatim}
2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-09}

@@

\begin{verbatim}
Run previous step: ./GHI_enh_03_process.R
\end{verbatim}

Attaching package: 'timetk'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:data.table':

    :=
\end{verbatim}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

Call:
stats::lm(formula = .formula, data = df)

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14

aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
inpatern
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
torun
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
2024-04-09 13:15:00.5 athan@tyler GHI_enh_03_process.R 22.842565 mins
\end{verbatim}

@@

Arima: -0.013183 +/- 6.904159

@@

Arima: 1.03413 +/- 0.363491

@@

Arima: 0.944623 +/- 0.387039

@@

Arima: 33.721354 +/- 8.881459

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-9} \end{center}

@@

\begin{verbatim}
2024-04-09 13:17:00.8 athan@tyler GHI_enh_03_process.R 1.962400 mins
\end{verbatim}
